\documentclass[11.5pt]{report}

% Geometry settings for margin
\usepackage{geometry}
\geometry{a4paper, margin=.25in}  

% Fancy headers
\usepackage{fancyhdr}

% Graphics
\usepackage{graphicx}

% Hyperlinks (load last to prevent conflicts)
\usepackage{hyperref}

% Enumeration customization
\usepackage{enumitem}

% Math symbols
\usepackage{amssymb}
\usepackage{amsmath}

% Special symbols and icons
\usepackage{fontawesome}

% Multicolumn formatting
\usepackage{multicol}

% Color options
\usepackage[x11names]{xcolor}

% Tables, multirow, and arrays
\usepackage{multirow}
\usepackage{array}
\usepackage{adjustbox}

% Text boxes and highlighting
\usepackage[most]{tcolorbox}

% Option to strike through text
\usepackage{ulem}

% UTF-8 support
\usepackage[utf8]{inputenc}

% Title formatting
\usepackage{titlesec}

% Font style
\usepackage{mathptmx}  % Times New Roman-like font

% Line spacing
\usepackage{setspace}
\onehalfspacing

% Microtype for better spacing
\usepackage{microtype}

% Justification options
\usepackage{ragged2e}

% Code listings
\usepackage{listings}
\lstset{breaklines=true}

% Array package for better table formatting
\usepackage{array}

\usepackage{lineno}[switch]
\usepackage{dirtree} % For directory trees

\usepackage{longtable} %loooong looong man

\usepackage{hyperref} %linking between documents
\tcbuselibrary{breakable} %Breakin boxes % For custom headers/footers


\pagenumbering{gobble}  
\title{Gerald's Zettelkasten}
\author{Gerald Amiel}
\date{\today}

\begin{document}
	
	\maketitle
	\tableofcontents
	\listoffigures
	\listoftables
	
	\newpage

\section*{Inbox}
Information dump while the thoughts are still fresh. 

\chapter*{General Overview}
\section*{Introduction}

This is simply an information dump of all the questions and ideas and questions that burn through my mind. A mind-palace if you will, to connect all my ideas into a cohesive-interlinked framework.  

\part{Open Questions}
\pagestyle{fancy}
\setlength{\headheight}{14pt}
\fancyhf{Open Questions}
\rhead{}
\lhead{}
\cfoot{\thepage}
\pagenumbering{arabic}
\setcounter{page}{1} 
\chapter{Bioinformatics}
\section{Metagenomics}
\subsection{Coverage, Depth, Sequencing}
\subsubsection{Further Investigations}
One may create a plot of genome size vs coverage 
\subsection{The deal with spiking}
\begin{itemize}
	\item How much spiking should be done? -- most papers only give a ballpark percentage of the community (which I presume requires prior optimization and re-optimization until it becomes the 1\% threshold they are after)
	\item Which is better? To choose spike that can be representative of the sequence? or to choose a spike that is completely unrelated to the environment you are sampling?
	\item Why does GC skew matter here? What does it really show? Inefficacy of the sequencing platform? -- How might we test this?
\end{itemize}
\subsection{How much DNA should is representative of a site?}
\subsection{How many reads do we need per site?}
\subsubsection{Further Investigations}
Meta-analysis per journal based on IF perhaps? too subjective? \\
"Tapering-off" analysis \\
Power Analysis \\
Sequence Space Exploration
\begin{itemize}
	\item Start with alleles of the protein-homologues or SNP sequence space
\end{itemize}


\chapter{Hydrodynamics}
\section{Flow and effluents}
\subsubsection{Metro Manila}
Which effluents flow directly into the Pasig River? Tullahan? Other River systems? \\
What tributaries specifically though? \\
What is the flow of these tributaries? Can we simulate them? \\
Can we have access to the underground sewage system? \\


\chapter{Legal}


\chapter{Philosophical/Theological}


\part{Notable Information}
\chapter{Batch effects}
\section{"Technician Bias"}





\part{Cookbook}
\chapter{The conundrum of biological sequences}
\section{Entropy-based analysis}
The idea here is that biological systems are essentially highly-optimized to maximize entropy in the Universe -- it has to if has to retain it's order. Given that part of that increase in entropy, is released from massive amounts of heat generated from the \texttt{The Central Dogma of Molecular Biology} itself and its maintenance, information entropy comes into play. 

\section{Evolutionary Tensor Landscape}

\section{Automation for RSS feeds}

\section{Jupyter in Lectures and Workshops}

\section{Amplifying Caffeine}
\subsection{Background: Caffeine and Adenosine}
Caffeine is an adenosine receptor antagonist (particularly subtypes A1 and A2). This is competitive binding, meaning both molecules \textit{compete} for a "spot" on the receptor -- which is important to note here because \textbf{caffeine does not displace adenosine once it's bound}, increasing caffeine intake merely increases the \textbf{likelihood of it binding to more receptors vs adenosine} -- or in biochemical speak, increases [ES] or the ligand-enzyme complex. \\
Ultimately this means that when you already have a lot of adenosine bound to its receptor, adding more caffeine won't displace them and will do little to counter the large degree of sleep pressure you experience. \\
Another consequence of this is as long as caffeine is in your system, once the adenosine either dissociates or is metabolized, caffeine starts binding - and only then, does it prevent adenosine from binding. \textbf{In a sense think of it this way, caffeine does not destroy sleep pressure, it slows down it's build-up.} \\
So I think you already have an idea of what we are cooking today, what if -- we get rid of adenosine itself. 

\subsection{Metabolism of Adenosine}
The main pathway I am looking at here is the stepwise dephosphorylation of ATP → ADP → AMP → Adenosine -- which is necessary for many metabolic processes most often as part of a coupled reaction. \textbf{The cooking part is} to leverage \texttt{Le Chatelier's Principle} i.e. drain ATP which either 
\begin{itemize}
	\item Reverses the reaction
	\item Depletes the production of Adenosine via this pathway
\end{itemize}
\noindent For example, one may donate blood before drinking caffeine. Donating blood was used as an example as it is considered safe (relatively, depending on how healthy you are of course) -- but draining blood in the body leads to erythropoiesis, leucopoiesis,, cytokine signaling, platelet activation and tissue repair (for the needle wound) -- all requiring large amounts of ATP. While RBCs may not contain nuclei, their precursors do and what do nuclei have? A LOT of DNA, and DNA replication is a massive ATP sink.  \\

\noindent \textbf{Disclaimer} please don't donate blood then start deadline lifting, you'll faint from hypotension lmao. 

\noindent \textbf{Other ways to drain ATP indirectly}
\begin{enumerate}
	\item Ion transport pumps that convert ATP free energy into electrochemical gradients
		\begin{itemize}
			\item Na/K ATPase pumps
			\item SERCA Ca\textsuperscript{2+} 
		\end{itemize}
	\item Uncoupling proteins (UCPs) in the mitochondria -- think brown fat ([TBA])
	\item 
\end{enumerate}




\noindent But there are also two other ways via elimination of Adenosine itself 
\begin{itemize}
	\item \textbf{Adenosine deamination} \\
	Adenosine → Inosine → Hypoxanthine → Xanthine → Uric Acid 
	\item \textbf{Adenosine Phosphorylation} (back to AMP)
\end{itemize}
Now the problem with using the first one is that high-levels of uric acid can lead to kidney stones and gout (need to check the literature on the direction of causality on this one [TBA]).


\noindent Another obvious side-effect is that for some individuals, it might exacerbate restlessness, anxiety, and/or insomnia. \textbf{But speaking of increasing insomnia}, \texttt{Russian sleep experiment creepypasta} anyone? Increased metabolic stress may also play a significant role -- especially for something like (glycolysis inhibition like shunting everything into PPP). 

\noindent And as with all drugs, the body will likely overcompensate (if a drug or cocktail is created), that would lead to dependence -- this is not your normal caffeine crash since the body might respond by increasing the adenosine receptors at a higher rate (need to research destroying vs inhibition on enzyme overproduction [TBA]). 

\noindent Moderate AMPK activation

\subsection{Theoretical use case}
Places wherein you would need emergency wakefulness such as space travel or military operations. 

If you were to use the AMPK activation pathway, this could lead to weight loss (which may be unwanted and uncontrolled) -- due to your body in heightened catabolic state. 





\subsection{Further Questions}
How does it differ from injecting people with adrenaline? \\
How would affect drunk drivers? Will the increased alertness be enough to mitigate the effects of alcohol? \\





\chapter{Data visualizations}
\section{The Hive visualization}
\section{Raw reads Manhattan}
Sites vs E-value (because it's more dependent on reference database than P-values)



\chapter{A Zettelkasten for scripts}
Just pull, the strings themselves, are a pipeline. 

	
\end{document}
